---
title: "Data Quality: Comparing Current versus Reference"
execute:
  echo: false
format:
  dashboard:
    theme: sandstone
    
params:
  current_id: 20240105
  reference_id: 20231205
  split_char: "_"
  hierarchy: ["site", "part"]
---

```{r}
#| label: load-packages
#| message: false
library(duckdb)
library(crosstalk)
library(DT)
library(dplyr)
library(ggplot2)
library(plotly)
library(xlsx)

number <- scales::number_format(big.mark = ",")
con <- dbConnect(duckdb(), dbdir = "../data/local.duckdb", shutdown=TRUE)

############################################################################################
# Statistical values for Value Boxes
# Critical statistics
n_with_deviation <- dbGetQuery(con, "SELECT COUNT(*) AS n FROM data_quality_statistics_current_reference WHERE ABS(ttest) > 0")
n_with_deviation = n_with_deviation$n

# Medium
n_with_warning <- dbGetQuery(con, "SELECT COUNT(*) AS n FROM data_quality_statistics_current_reference WHERE ABS(ttest) > 1.0 AND ABS(ttest) < 1.64")
n_with_warning = n_with_warning$n

n_with_danger <- dbGetQuery(con, "SELECT COUNT(*) AS n FROM data_quality_statistics_current_reference WHERE ABS(ttest) >= 1.64")
n_with_danger = n_with_danger$n
############################################################################################


############################################################################################
# Extract statistics table for medium and critical forecast items
statistics_critical_tbl <- dbGetQuery(con, "SELECT * FROM data_quality_statistics_current_reference WHERE ABS(ttest) > 1.0") |>
    select(-n, -start_date, -end_date) |>
    mutate(category = ifelse(abs(ttest) <= 1.64, "Medium", "Critical"),
           color    = ifelse(category == 'Medium', "#af8e08", "#d9534f"))

# Shared object
statistics_critical_tbl <- SharedData$new(statistics_critical_tbl |>   mutate(id = paste0(site, "_", part)), ~id, group="ts_selection")
############################################################################################


############################################################################################
# Query & prepare timeseries data
joined_tbl <- dbGetQuery(con, "SELECT * FROM staging_joined_req_del")

joined_tbl = joined_tbl |>
  dplyr::left_join(statistics_critical_tbl |> select(site, part, ttest), by=c("site", "part")) |>
  filter(!is.na(ttest)) |>
  mutate(id = paste0(site, "_", part)) |>
  filter(date <= "2023-11-01") |>
  select(-ttest)

# Shared object
joined_tbl <- SharedData$new(joined_tbl, ~id, group="ts_selection")
############################################################################################


############################################################################################
# Number of Keys in Current & Reference
n_keys_intersection <- dbGetQuery(con, "SELECT COUNT(*) FROM data_quality_statistics_current_reference")
n_keys_intersection = n_keys_intersection$n

res <- dbGetQuery(con, "SELECT * FROM missing_keys_current")
missing_keys_current_tbl <- SharedData$new(res)

res <- dbGetQuery(con, "SELECT * FROM missing_keys_reference")
missing_keys_reference_tbl <- SharedData$new(res)
############################################################################################


############################################################################################
# Excel Export of Statistics
file_name = paste0(".quarto/output/", params$current_id, "_", params$reference_id, " Data Quality Statistics.xlsx")
write.xlsx(statistics_critical_tbl$origData() |> select(-color, -id), file_name, sheetName = "MUH", col.names = TRUE, row.names = FALSE, append = FALSE)
############################################################################################

dbDisconnect(con, shutdown=TRUE)
```


#  {.sidebar}
This dashboard displays statistics for comparing the input & output of the current versus the reference run:

| Parameter      | Value                     |
|----------------|---------------------------|
| **Current**    | `  `r params$current_id` `|
| **Reference**  |` `r params$reference_id` `|

------------------------------------------------------------------------

**Statistic Parameters**

| Parameter    | Value |
|-------------------------|----------------------|
| **T-Stat for Medium**   | `1.0 < T <= 1.64`    |
| **T-Stat for Critical** | `1.64 < T`           |

------------------------------------------------------------------------

**Kärcher Specific Parameters**

The datasets are filtered as follows:

| Parameter    | Value                   |
|--------------|-------------------------|
| **Category** | `RequestedDeliveryDate` |
| **QTY**      | `Corrected`             |
| **PiPo**     | `FALSE`                 |

------------------------------------------------------------------------


# Deviations in Forecast Items

## Row

```{r}
#| content: valuebox
#| title: "Number of Deviations"

list(
  icon = "info-circle",
  color = "primary",
  value = number(n_with_deviation)
)
```
```{r}
#| content: valuebox
#| title: "Number of Medium Deviations"

list(
  icon = "exclamation-circle",
  color = "warning",
  value = number(n_with_warning)
)
```

```{r}
#| content: valuebox
#| title: "Number of Critical Deviations"

list(
  icon = "x-circle",
  color = "danger",
  value = number(n_with_danger)
)
```

## Row

## Column

```{r}
#| title: Test Statistics for Medium & Critical Deviations

statistics_critical_tbl |>
  datatable(rownames = FALSE,
    options = list(
      dom = "lrtip", 
      paging = FALSE,
      pageLength = 25, 
      scrollY = FALSE,
      selection = "single"
    ),
     filter = list(position = 'top', clear = FALSE)
  ) |>
  formatRound(columns=c("mean_current", "mean_reference", "std_current", "std_reference", "mean_difference", "ttest"))
```

## Row

### Column {.tabset width="50%"}

```{r}
#| title: Demand Series
plot_ly(joined_tbl, x = ~date, y=~current_qty, type = 'scatter', mode = 'lines', name = "Current") |>
  plotly::add_lines(x = ~date, y=~reference_qty, name="Reference") |>
  highlight(opacityDim = 0) |>
  layout(yaxis = list(matches = "y"))
```

```{r}
#| title: Deviations by Site
statistics_critical_tbl$origData() |>
  group_by(site) |>
  count() |>
  ungroup() |>
  arrange(-n) -> site_plots_tbl

top_sites = site_plots_tbl$site

statistics_critical_tbl$origData() |>
  filter(site %in% site_plots_tbl$site) |>
  group_by(site, category, color) |>
  count() |>
  ungroup() |>
  arrange(-n) -> site_plots_tbl

site_plots_tbl$site = factor(site_plots_tbl$site, levels = rev(top_sites))



site_plots_tbl |>
 plotly::plot_ly(
      x = ~n,
      y = ~site,
      color= ~ category,
      colors = c(Medium = '#af8e08', Critical = '#d9534f'),
      type = "bar",
      orientation = "h"
    ) |>
    plotly::layout(
      xaxis = list(title = ""),
      yaxis = list(title = "", ticksuffix = " ", tickfont = list(size = 10)), 
      barmode = 'stack'
    ) |>
    plotly::config(displayModeBar = F)
```


### Column

```{r}
#| title: KPIs
plot_ly(statistics_critical_tbl, 
      x = ~mean_difference, 
      y=~ttest, 

      marker = list(
        size = ~ abs(mean_difference),
        group    = ~category,
        color   = ~ color,
        fill   = ~ color,
        line = list(width=0),
        sizeref = 1,
        sizemode = 'area',
        opacity = 0.4
      )
    ) %>%
  layout(
    autosize = TRUE,
    xaxis = list(
      zeroline = TRUE,
      ticks = "outside",
      tickcolor = "#fff",
      tickformat = "+",
      tickfont = list(size = 14),
      titlefont = list(family = "Open Sans",
                       size = 20),
      title = "Mean(Current) - Mean(Reference)"
    ),
    yaxis = list(
      zeroline = TRUE,
      ticks = "outside",
      tickcolor = "#fff",
      tickformat = "+",
      tickfont = list(size = 14),
      titlefont = list(family = "Open Sans",
                       size = 20),
      title = "T-Statistic"
    ),
    hoverlabel = list(font = list(family = "Open Sans",
                                  size = 16))
  )
```



# Added/Removed Forecast Items

## Row

```{r}
#| content: valuebox
#| title: "Number of Forecast Items in Current & Reference"

list(
  icon = "exclamation-circle",
  color = "info",
  value = number(n_keys_intersection)
)
```

```{r}
#| content: valuebox
#| title: "Number of Missing Forecast Items in Current"

list(
  icon = "x-circle",
  color = "danger",
  value = number(nrow(missing_keys_current_tbl$origData()))
)
```

```{r}
#| content: valuebox
#| title: "Number of Missing Forecast Items in Reference"

list(
  icon = "plus-circle",
  color = "success",
  value = number(nrow(missing_keys_reference_tbl$origData()))
)
```


## Row {height="40%"}

### Column {.tabset}

```{r}
#| title: Missing Keys in Current

missing_keys_current_tbl |>
  datatable(
    rownames = FALSE,
    options = list(
      dom = "lrtip", 
      pageLength = 25, 
      scrollY = TRUE
    ),
  )
```


```{r}
#| title: By Site
missing_keys_current_tbl$origData() |>
  group_by(site) |>
  count() |>
  ungroup() |>
  arrange(-n) -> site_plots_tbl

top_sites = site_plots_tbl$site

site_plots_tbl$site = factor(site_plots_tbl$site, levels = rev(top_sites))


site_plots_tbl |>
 plotly::plot_ly(
      x = ~n,
      y = ~site,
      fill= '#d9534f',
      type = "bar",
      orientation = "h"
    ) |>
    plotly::layout(
      xaxis = list(title = ""),
      yaxis = list(title = "", ticksuffix = " ", tickfont = list(size = 10))
    ) |>
    plotly::config(displayModeBar = F)
```


### Column {.tabset}

```{r}
#| title: Missing Keys in Reference

missing_keys_reference_tbl |>
  datatable(
    rownames = FALSE,
    options = list(
      dom = "lrtip", 
      pageLength = 25, 
      scrollY = TRUE
    )
  )
```

```{r}
#| title: By Site
missing_keys_reference_tbl$origData() |>
  group_by(site) |>
  count() |>
  ungroup() |>
  arrange(-n) -> site_plots_tbl

top_sites = site_plots_tbl$site

site_plots_tbl$site = factor(site_plots_tbl$site, levels = rev(top_sites))

site_plots_tbl |>
 plotly::plot_ly(
      x = ~n,
      y = ~site,
      fill="#93c54b",
      type = "bar",
      orientation = "h"
    ) |>
    plotly::layout(
      xaxis = list(title = ""),
      yaxis = list(title = "", ticksuffix = " ", tickfont = list(size = 10))
    ) |>
    plotly::config(displayModeBar = F)
```
