---
title: "Made-Up History"
execute:
  echo: false
format:
  dashboard:
    theme: sandstone
    
params:
  current_id: 20240105
  reference_id: 20231205
---

```{r}
#| label: load-packages
#| message: false
library(duckdb)
library(crosstalk)
library(DT)
library(dplyr)
library(ggplot2)
library(plotly)
library(tidyr)
library(xlsx)

number <- scales::number_format(big.mark = ",")

con <- dbConnect(duckdb(), dbdir = "../data/local.duckdb", shutdown=TRUE)
statistics_tbl <- dbGetQuery(con, "SELECT * FROM madeuphistory_vs_requested_delivery_date")

dbDisconnect(con, shutdown=TRUE)


statistics_tbl = statistics_tbl |>
  mutate(muh_qty_rdd_qty = muh_qty / rdd_qty,
         full = muh_qty + rdd_qty,
         muh_perc = muh_qty / full, 
         rdd_perc = rdd_qty / full) |>
  rename(`Made-Up History Qty` = muh_qty,
         `Requested Delivery Date Qty` = rdd_qty,
         `Made-Up History Qty / Made-Up History Qty` = muh_qty_rdd_qty) 

file_name = paste0(".quarto/output/", params$current_id, "_", params$reference_id, " Made-Up History.xlsx")
write.xlsx(statistics_tbl |> select(site, part, `Made-Up History Qty`, `Requested Delivery Date Qty`, `Made-Up History Qty / Made-Up History Qty`), file_name, sheetName = "MUH", col.names = TRUE, row.names = FALSE, append = FALSE)
```


#  {.sidebar}
This dashboard displays statistics for comparing the input & output of the current versus the reference run:

| Parameter      | Value                     |
|----------------|---------------------------|
| **Current**    | `  `r params$current_id` `|
| **Reference**  |` `r params$reference_id` `|

------------------------------------------------------------------------

**Statistic Parameters**

| Parameter    | Value |
|-------------------------|----------------------|
| **T-Stat for Medium**   | `1.0 < T <= 1.64`    |
| **T-Stat for Critical** | `1.64 < T`           |

------------------------------------------------------------------------

**Kärcher Specific Parameters**

The datasets are filtered as follows:

| Parameter    | Value                   |
|--------------|-------------------------|
| **Category** | `RequestedDeliveryDate` |
| **QTY**      | `Corrected`             |
| **PiPo**     | `FALSE`                 |

------------------------------------------------------------------------


# Deviations in Forecast Items

## Row

```{r}
#| content: valuebox
#| title: "Number of Forecast Items with MUH"

list(
  icon = "info-circle",
  color = "info",
  value = number(nrow(statistics_tbl))
)
```


## Row

## Column

```{r}
#| title: Test Statistics for Medium & Critical Deviations

statistics_tbl |>
  datatable(rownames = FALSE,
            extensions = "Buttons", 
    options = list(
      dom = "lrtip", 
      paging = FALSE,
      pageLength = 25, 
      scrollY = FALSE,
      selection = "single"
    ),
     filter = list(position = 'top', clear = FALSE)
  ) |>
  formatPercentage(columns="Made-Up History Qty / Made-Up History Qty")
```
